---
title: "2020MQ044_QC"
date: "`r Sys.Date()`"
output:
    html_document:
      code_folding: hide
      toc: true
      toc_depth: 2
      highlight: tango
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = file.path(dirname(inputFile), '2020MQ044.html')) })

---


```{r setup_packages,  echo=FALSE, cache=FALSE, warning= FALSE, message=FALSE}
#method = "DDA  MBR"
pacman::p_load("knitr","readr","tidyverse", "openxlsx", "stringr",
               "data.table","BiocManager","openxlsx","factoextra", "devtools",
               "DescTools", "UpSetR", "magick", "proteus","SubCellBarCode")

source_file_name <- here::here("Codes",
                               "functions.R")
test_file(here::here(
    "Codes",
    "tests",
    "testthat",
    "test_functions.R"
))
source(source_file_name)

file_parsed = parse(source_file_name) %>% 
    Filter(is_function, .)  
unlist(Map(function_name, file_parsed))

## Global options
options(max.print="75")
opts_chunk$set(cache=FALSE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
#opts_knit$set(root.dir = "./../")
```

We see that there are almost no proteins/peptides identified in the chrom_231,  and very few in the SS alone. This is mostly likely because of the extra node which only targets the Silac pairs meaning that the methodology works and there are no silac pairs in the unlabelled Chrom and very few pairs in the SS probably due to incomplete incorporatio.



```{r loading_maxquant, fig.width = 14, fig.height=14}
txt_folder <-  here::here("Datasets", "Raw",
                            "2020MQ044txt",
                            "txt")
Quality_Control(txt_folder)
condition_names <-  c(paste0("control_",1:3),
                      paste0("sh_1_",1:3),
                      paste0("sh_2_",1:3))
samples_ids <-  1:9
measure_col <-  "Intensity"


proteus_loading <- load_MaxQuant(txt_folder,
                                        measure_col,
                                        samples_ids,
                                        condition_names)


#proteus::plotCount(proteus_loading$peptides)
protein_groups <-  proteus_loading$proteins[["stats"]]%>%
    dplyr::select(-variance,-ngood) %>%
    mutate(Uniprot = str_match(id,"sp\\|([:graph:]*?)\\|")[,2],
           mean_log2 = log2(mean)) 
protein_groups %>% na.omit() %>% count(condition) %>% 
    ggplot(aes(x = condition, y = n)) +
    geom_col() + ggtitle("Proteins_per_condition")


HUMAN_9606 <- read_tsv(here::here("Datasets","Raw","HUMAN_9606_idmapping.dat"),
                 col_names = FALSE) 

HUMAN_9606_idmapping <- HUMAN_9606 %>% filter(X2 == 'Gene_Name')
Wider_df <- protein_groups %>%# ungroup() %>% #distinct(condition, Uniprot, .keep_all = TRUE) %>%  
    pivot_wider(id_cols = Uniprot, names_from = "condition", values_from = "mean_log2") 

```
We will use the qvalue package for multiple-testing correction (after looking at what the distribution of the p_values looks like) and the
https://www.bioconductor.org/packages/release/bioc/vignettes/qvalue/inst/doc/qvalue.pdf
